% Sample Resume (sample.tex)
% github.com/stackptr/resume-tex

% Use resume.cls style
\documentclass{resume}
\usepackage{hyperref}
%------------------------------------------------------------------------------
%	Header
%------------------------------------------------------------------------------

% Name and contact information
\name{Spencer Delcore}
\coop{Computer Engineering - University of Waterloo}
\contact{261-130 Columbia Street West \\ Waterloo ON, N2L 0G6}
\contact{(416) 453~$\cdot$~2755 \\ sdelcore@uwaterloo.ca \\ \href{http://sdelcore.github.io}{sdelcore.github.io}}
\begin{document}

%----------------------------------------------------
%	Skills section
%----------------------------------------------------

\begin{rSection}{Qualifications}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% ---------------------------------------------------
%	Languages subsection
% ---------------------------------------------------
Languages & 
    C++, Python, C, C\#, VHDL/Verilog, MATLAB, PHP, JavaScript\\
% ---------------------------------------------------
%	Technologies subsection
% ---------------------------------------------------
Frameworks/Technologies & 
     Azure IoT Edge, Qt, Git, Unity, AWS, SQL, Yocto, Buildroot\\

Embedded Experience &
	 QNX, UNIX, Arduino, Raspberry Pi, Avnet MiniZed, Renasas R-Car-H3

\end{tabular}

\end{rSection}

%----------------------------------------------------
%	Projects Section
%----------------------------------------------------
\begin{rSection}{Work Experience}
%Molex
\begin{rSubsection}{Molex. -\em{ Co-op Developer}}
{Sept. 2018 - Dec. 2018}{Waterloo, ON}{ }
\item Responsible for evaluating QNX Hypervisor on an Intel NUC and Renasas R-Car-H3 
\item Built various Linux images using both Yocto and Buildroot, along with sample programs in C
\item Developed an Edge Gateway for PROFINET enabled devices using Azure IoT Edge
\item Designed a Human Machine Interface (HMI) connected to an OPC Server
\end{rSubsection}
%Evertz
\begin{rSubsection}{Evertz Microsystems Ltd. -\em{ Embedded Systems Design Engineering, Co-op}}
{Sept. 2017 - Dec. 2017}{Burlington, ON}{ }
\item Developed a multi-threaded framework for generating embedded user interfaces using Qt and QML
\item Implemented an embedded SQLite database, and configured it for performance
\item Communicated through a defined protocol with various systems via D-Bus 
\item Parsed multiple JSON structures to generate various user interfaces
\end{rSubsection}
% CSC
\begin{rSubsection}{Cognitive Systems Corp. -\em{ Augmented Reality (AR) Developer, Co-op}}
{Jan. 2017 - April. 2017}{Quantum Valley Investments, Waterloo, ON}{ }
\item Responsible for creating an AR demonstration to visualize wireless signals using a Microsoft HoloLens
\item Dynamically generated interactive holograms using Unity and C\#
\item Created a Python program that interfaces with Cognitive's system on a chip (SoC) to detect wireless signals
\item Implemented websockets to communicate between the SoC and the HoloLens
\end{rSubsection}

% INGLE
\begin{rSubsection}{Ingle International Inc. -\em{ Software Engineering, Co-op}}
{May. 2016 - Aug. 2016}{Toronto, ON}{ }
\item Accountable for building and maintaining version two of their API using PHP and the Laravel framework
\item Built a dynamically themed Android application using Java and React Native
\item Researched, presented, and participated in critical development meetings
\end{rSubsection}

% VIZIYA
\begin{rSubsection}{VIZIYA -\em{ Software Developer, Co-op}}
{Sept. 2015 - Dec. 2015}{Waterdown, ON}{ }
\item Designed and developed quality ASP.NET and C\# applications
\item Preformed SQL queries to retrieve and manipulate data from Oracle and SAP databases
\item Generated user guides, training manuals, and documentation
\end{rSubsection}

% ESIG
\begin{rSubsection}{Emerging Star Investment Group -\em{ Software Developer, Co-op}}
{Jan. 2015 - April 2015}{Accelerator Centre, Waterloo, ON}{ }
\item Developed financial web-based software using PHP and the Laravel framework
\item Created and maintained an Amazon Web Services (AWS) EC2 server to host the company website
\item Built scripts to scrape and store financial related data using Python
\end{rSubsection}

\end{rSection}

\pagebreak  
\vspace*{20px}
%----------------------------------------------------
%	Projects Section
%----------------------------------------------------
\begin{rSection}{Projects}

\begin{rSubsection}{MIPS Processor -\em{ Verilog}}
{2018}{}{}
\item Designed and implemented a cycle-accurate MIPS processor architecture in Verilog
\item Constructed each stage of the 5-stage pipelined design using the synthesizable subset of verilog at the register-transfer level (RTL)
\item Made use of testbenches and debugging strategies to ensure correctness and completeness
\end{rSubsection}

\begin{rSubsection}{VHDL Compiler -\em{ Java, VHDL}}
{2017}{}{}
\item Created a VHDL synthesizer and simulator using Java
\item Uses VHDL (combinational circuits only) as the input language and produces circuit diagrams and simulations
\item Gathered important compiler concepts such as regular languages, regex, DFA, lexing, recursive decent parsing, and context-free grammars
\end{rSubsection}

\begin{rSubsection}{Room Sensors -\em{ C++, Python, Bash, JavaScript}}
{2017}{}{}
\item Plots information stored in a database containing data from Arduino sensors
\item Communicate and store sensor data from an Arduino to a Raspberry Pi using a created serial protocol
\item Chart data from JSON reports received from a Raspberry Pi through websockets
\item Created an install script that sets up the websocket, web page, cron job, Arduino, and MySQL database
\end{rSubsection}

\begin{rSubsection}{DAC Audio Player -\em{ Altera FPGA, C}}
{2016}{}{}
\item Implemented a 16-bit sampling stereo digital to analog audio player with push buttons to control playback
\item Gained experience with Altera audio IP core, audio sampling and buffering, and interrupts
\item Made use of the FatFS CLI to mount and interpret WAV files from a microSD card
\end{rSubsection}

\end{rSection}

%------------------------------------------------------------------------------
%	Education section
%------------------------------------------------------------------------------

%\begin{rSection}{Education}

%{\bf University of Waterloo, Waterloo, Ontario} \hfill {2014 - Present} \\
%Candidate for Bachelor of Applied Science, Computer Engineering, Honours, Co-op

%{\bf Carleton University, Ottawa, Ontario} \hfill {2013 - 2014} \\
%Candidate for Bachelor of Applied Science, Computer Engineering \\
%\textit{Computer Engineering GPA:} $10.9/12$

%\end{rSection}


\end{document}
