% Sample Resume (sample.tex)
% github.com/stackptr/resume-tex

% Use resume.cls style
\documentclass{resume}

%------------------------------------------------------------------------------
%	Header
%------------------------------------------------------------------------------

% Name and contact information
\name{Spencer Delcore}
\coop{Honours Computer Engineering 3A - 20521263}
\contact{1 Columbia Street West \\ Waterloo, Ontario, N2L 0A8}
\contact{(416) 453~$\cdot$~2755 \\ sdelcore@uwaterloo.ca \\ sdelcore.github.io}
\begin{document}
\begin{rSection}{}\end{rSection}

\{DATE\}\\
\{COMEPANY NAME\} \\
\{COMPANY ADDRESS\}t\\
\{CITY\}, ON \{POSTAL CODE\}\\

To Whom It May Concern,
\par
\hspace{36pt}
My name is Spencer Delcore and I am applying for the position of {\{JOB NAME\}} for the \{TERM\} of \{YEAR\}. I am currently a third year student in Computer Engineering at the University of Waterloo. I previously completed four co-op jobs, each at a different company in various stages of the business life cycle. These opportunities have allowed me to gain practical experience on the business and the technology side of each company. By applying my communication, problem-solving, and technical skills, I believe I would be a strong asset to \{COMPANY NAME\}.

\hspace{36pt}
My introduction to working in the technology field was in the winter of 2015, while working for Emerging Star Investment Group, a SaaS start-up company based in Waterloo. As the only person on their technical team, I was quickly given full responsibility of all projects and infrastructure. I developed my communication skills while preparing and presenting all major decisions and progress to groups who were not proficient in the field. In the summer of 2016, while working for Ingle International, I was able to further hone my communication skills. While working together as a team of developers, we ensured deadlines and project specifications were met successfully and completed despite short timeframes.

\hspace{36pt}
I have experience with many aspects of technology, such as full stack development for both web and mobile devices, embedded systems, and creating infrastructures for both personal and professional use. Having such broad experience, I am able to adapt to any situation without being overwhelmed. When placed outside of my expertise, I employ every available resource to meet and exceed expectations. I enjoy facing new challenges and being able to apply my learnings. I understand that not all problems require the same approach. I am willing to investigate and develop new solutions, and improve on existing ones.

\hspace{36pt}
Building on my experience in development, I am excited to further explore \{WHAT COMPANY DOES\}. \{COMPANY NAME\} is one of the leading open-source operating system developers has paved a path in the technology sector. I hope to learn from \{COMPANY NAME\}'s vast technological expertise while also contributing to \{COMPANY NAME\}'s history of success. I believe that working with \{COMPANY NAME\} will complement my experience, skills, and educational trajectory.

\hspace{36pt}
Thank you for taking the time to consider my application. I look forward to hearing from you.

Sincerely,

Spencer Delcore

\end{document}
